Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2020-10-26 paper/main.tex
WJC - introduction paragraph 2

Typically, stars are modelled on a star-by-star basis with assumptions made about the bulk physical quantities based on empirical relations or solar calibrations. For instance, a helium ($Y$) to heavy-element ($Z$) ratio ($\Delta Y / \Delta Z$) and mixing-length theory parameter ($\mlt$) are assumed. However, there has been little effort to account for the population distribution of such quantities. Assuming $Y$ and $\mlt$ can result in inaccurate inference and systematics \citep{Valle.DellOmodarme.ea2015}. Independently modelling $Y$ and $\mlt$ can also be computationally demanding and requires high-precision observations in order to return meaningful stellar properties.

>>>>

Typically, stars are modelled on a star-by-star basis with estimates of stellar properties including some assumptions handled by simple scaling relations and solar calibrations. % assumptions made about the bulk physical quantities based on empirical relations or solar calibrations. 
For instance, a helium ($Y$) to heavy-element ($Z$) ratio ($\Delta Y / \Delta Z$) and mixing-length theory parameter ($\mlt$) are often assumed. However, there has been little effort to account for the population distribution of such quantities. Assuming $Y$ and $\mlt$ can result in inaccurate inference and systematics \citep{Valle.DellOmodarme.ea2015}. Independently modelling $Y$ and $\mlt$ can also be computationally demanding and requires high-precision observations in order to return meaningful stellar properties.
